Untwisting the Tetrahelix (v0.4)

### 2017-02-16 doc/TetrahelixUntwist.tex
fixed a major problem in my distance formula, now ready to try optimality again, and eventually code

\begin{align*}
  1^2 &= d^2 + (2 r \sin{ \rho / 2})^2 \\
  1 &= d^2 + 4 r^2 (\sin{ \rho / 2})^2 
\end{align*}

@@

\begin{align*}
  \text{one-hop} &= dist(H_{general}(n,c,\rho,h_{\rho}),H_{general}(n,c+1,\rho,d_{\rho}),r_{\rho})  \\
  \text{one-hop} &= dist(H_{general}(0,0,\rho,h_{\rho}),H_{general}(0,1,\rho,d_{\rho},r_{\rho}))  \\  
  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (,r_{\rho}\sin(\rho(3\cdot 0 + 0)) - r_{\rho}\sin(\rho(3\cdot 0 + 1)+\frac{2\pi}{3}))^2  +
    (r_{\rho}\cos(\rho(3\cdot0+0)) - r_{\rho}\cos(\rho(3\cdot 0+1) + \frac{2\pi}{3})))^2} \\
  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (0  - r_{\rho}\sin(\rho + \frac{2\pi}{3}))^2  +
    (r_{\rho} - r_{\rho}\cos(\rho + \frac{2\pi}{3}))^2} \\
  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2\sin^2(\rho + \frac{2\pi}{3})  +
    r_{\rho}^2(1 - \cos(\rho + \frac{2\pi}{3}))^2} \\
  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2(\sin^2(\rho + \frac{2\pi}{3})  + (1 - \cos(\rho + \frac{2\pi}{3}))^2)} \\
\end{align*}

By similar algebra and trigonometry:
\begin{align*}
  \text{two-hops}  &= \sqrt{\frac{4d_{\rho}^2}{9} + r_{\rho}^2(\sin^2(\rho + \frac{2\pi}{3})  + (1 - \cos(\rho + \frac{2\pi}{3}))^2)} \\
\end{align*}

Let $f_{\rho} = \sin^2(\rho + \frac{2\pi}{3})  + (1 - \cos(\rho + \frac{2\pi}{3})^2$.

The expression $f_{\rho}$ is maximized when $\rho = 2\pi/6 = 60\degree$, so that
is in some sense the ``wildest'' rail angle which maximizes the lengths. Since this expression is increasing up until this angle,
we conclude that:
\begin{align*}
  \text{two-hops} - \text{one-hop}  &= \sqrt{\frac{4d_{\rho}^2}{9} + r_{\rho}^2f_{\rho}} - \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2f_{\rho}} 
\end{align*}

The analysis below here is incorrect because it doesn't take into account the change in $d_{\rho}$ with $\rho$. In the special case that
$\rho = 0$, the analysis is correct. Possibly I need to change to use two equations to try to find the optimal $\rho$ here.
In any case it must unify with the BC math!

Tomorrow try combining with our equation for $d_{\rho}$ to see if I can make it come out.

@@

\begin{align*}
  1 &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2(\sin^2(\rho + \frac{2\pi}{3})  + (1 - \cos(\rho + \frac{2\pi}{3}))^2)} \\
  r_{\rho} &= \frac{\sqrt{9-d^2}  }{3\sqrt{\sqrt{3}\sin(\rho) +\cos(\rho) + 2}}
\end{align*}
(where $\sqrt{3}\sin(\rho) +\cos{\rho} + 2 \neq 0$), which does not occur when $\rho \leq \pi/3$).

>>>>

\begin{align*}
  1^2 &= d^2 + (2 r \sin{ \rho / 2})^2 \\
  1 &= d^2 + 4 r^2 (\sin{ \rho / 2})^2 \\
  d^2 &= 1 - 4 r^2 (\sin{ \rho / 2})^2   
\end{align*}

@@

\begin{align*}
  \text{one-hop} &= dist(H_{general}(n,c,\rho,d_{\rho}),H_{general}(n,c+1,\rho,d_{\rho}),r_{\rho})  \\
  \text{one-hop} &= dist(H_{general}(0,0,\rho,d_{\rho}),H_{general}(0,1,\rho,d_{\rho},r_{\rho}))  \\  
  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (r_{\rho}\sin(\rho((1/3)\cdot 0 + 0)) - r_{\rho}\sin(\rho((1/3)\cdot 0 + 1)+\frac{2\pi}{3}))^2  +
    (r_{\rho}\cos(\rho((1/3)\cdot0+0)) - r_{\rho}\cos(\rho((1/3)\cdot 0+1) + \frac{2\pi}{3})))^2} \\
  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (0  - r_{\rho}\sin(\rho/3 + \frac{2\pi}{3}))^2  +
    (r_{\rho} - r_{\rho}\cos(\rho/3 + \frac{2\pi}{3}))^2} \\
  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2\sin^2(\rho/3 + \frac{2\pi}{3})  +
    r_{\rho}^2(1 - \cos(\rho/3 + \frac{2\pi}{3}))^2} \\
  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
  \text{but... } & d_{\rho}^2 &= 1 - 4 r_{\rho}^2 (\sin{ \rho / 2})^2 \\
  \text{one-hop}  &= \sqrt{\frac{1 - 4 r_{\rho}^2 (\sin{ \rho / 2})^2}{9} + r_{\rho}^2(\sin^2(\rho + \frac{2\pi}{3})  + (1 - \cos(\rho + \frac{2\pi}{3}))^2)} \\  
\end{align*}

To Be Done: I need to see if the one-hop formulat can be simplified.
Compute the two-hop formula and test that it gives length 1 when the BC constants. -- YES!

By similar algebra and trigonometry:
\begin{align*}
  \text{two-hops}  &= \sqrt{4\frac{1 - 4 r_{\rho}^2 (\sin{ \rho / 2})^2}{9} + r_{\rho}^2(\sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \\
\end{align*}

Note: it is not clear I am allowed to do this, because the two-hop function is different!

Let $f_{\rho} = \sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3})^2$.
Let $g_{\rho} = \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3})^2$.

The expression $f_{\rho}$ is maximized when $\rho = 2\pi/6 = 60\degree$, so that
is in some sense the ``wildest'' rail angle which maximizes the lengths. Since this expression is increasing up until this angle,
we conclude that:
\begin{align*}
  \text{two-hops} - \text{one-hop}  &= \sqrt{\frac{4d_{\rho}^2}{9} + r_{\rho}^2g_{\rho}} - \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2f_{\rho}} 
\end{align*}

To Be Done: I need to plot this expression, see if it has a maximum, and see if it always decreasing in this range, to see if we can prove optimality.

@@

\begin{align*}
  1 &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
  r_{\rho} &= \frac{2 \sqrt{2} }{\sqrt{9 \sqrt{3} sin(\rho/3) + 9 \cos(\rho/3) + 2 cos(\rho)+ 16 }}
\end{align*}
(where $9 \cos(\rho/3) + 2 cos(\rho)+ 16  \neq 0$), which does not occur when $\rho \leq \pi/3$).
